Inferring the existence and direction of causal associations in the face of measurement error

### 2017-02-18 docs/manuscript.tex
updated

An established study design that can provide information about causality
is randomisation. Given the hypothesis that trait A (henceforth referred
to as the exposure) is causally related to trait B (henceforth referred
to as the outcome), randomisation can be employed to assess the causal
nature of the association by randomly splitting the sample into two
groups, subjecting one group to the exposure and leaving the other as a
control. The association between the exposure and the outcome in this
setting provides a robust estimate of the causal relationship. This
provides the theoretical basis behind randomised control trials, but in
practice randomisation is often impossible to implement in an
experimental context due to cost, scale or inability to manipulate the
exposure. The principle, however, can be employed in extant
observational data through the use of genetic variants associated with
the exposure (instruments), where the inheritance of an allele serves as
a random lifetime allocation of differential exposure
levels\textsuperscript{15,16}. Two statistical approaches to exploiting
the properties of genetic instruments are widely used: mediation-based
approaches and Mendelian randomisation (MR).

@@

MR has some important advantages over the mediation-based approaches.
The mediation-based approaches require that the exposure, outcome and
instrumental variables are all measured in the same data, whereas recent
extensions to MR circumvent this requirement, allowing causal inference
to be drawn when exposure variables and outcome variables are measured
in different samples\textsuperscript{28}. This has the crucial advantage
of improving statistical power by allowing analysis in much larger
sample sizes, and dramatically expands the breadth of possible
phenotypic relationships that can be evaluated\textsuperscript{26}.
Additionally, when MR assumptions are satisfied the method is robust to
there being measurement error in the exposure variable. Indeed
instrumental variable (IV) analysis was in part initially introduced as
a correction for measurement error in the exposure\textsuperscript{29},
whereas it has been noted that both classic mediation-based
analyses\textsuperscript{13,14,30,31} and mediation-based methods that
use instrumental variables\textsuperscript{32,33} are prone to be
unreliable in its presence.

Using theory and simulations we show how non-differential measurement
error in phenotypes can lead to unreliable causal inference in the
mediation-based CIT method. We then present an extension to MR that
allows researchers to ascertain the causal direction of an association
even when the biology of the instruments are not fully understood, and
also a method to evaluate the sensitivity of the result of this
extension to measurement error. This improves the utility of MR in cases
where mediation based methods might have otherwise been used
preferentially. Finally, we apply this new method to infer the direction
of causation between DNA methylation levels and gene expression levels.
Our analyses highlight that because these different causal inference
techniques have varying strengths and weaknesses, triangulation of
evidence from as many sources as possible should be practiced in causal
inference\textsuperscript{34}.

@@

where \(\beta_{MR} \neq 0\) denotes the existence of causality, and the
\(\beta_{MR}\) is an estimate of the causal effect.

Measurement error of an exposure can be modeled as a transformation of
the true value that leads to the observed value, \(x_o = f(x)\). For
example, following Pierce and VanderWeele\textsuperscript{35} we can
define

@@

where \(\alpha_{mx}\) and \(\beta_{mx}\) influence the error in the
measurement of \(x\) by altering its scale, and \(\epsilon_{mx}\)
represents the imprecision (or noise) in the measurement of \(x\). The
same model of measurement error can be applied to the outcome variable
\(y\). In this study we assume there is no measurement error in the SNP.

@@

The method that we will now describe is able to distinguish between two
models, \(x \rightarrow y\) or \(y \rightarrow x\). Unlike the CIT
framework, this approach cannot infer if the true model is
\(x \leftarrow g \rightarrow y\). We also assume all genetic effects are
additive.

@@

The Steiger test for inferring if \(x \rightarrow y\) is based on
evaluating \(\rho_{gx} > \rho_{gy}\). However, \(\rho_{gx}\) and
\(\rho_{gy}\) are underestimated if \(x\) and \(y\) are measured
imprecisely. If, for example, \(x\) has lower measurement precision than
\(y\) then we might empirically obtain \(\rho_{g,x_o} > \rho_{g,y_o}\).
As we show in the appendix, the maximum measurement error of \(x_o\) is
\(\rho_{g,x_o}\) and the minimum is 0 (same applies to \(y_o\)). It is
possible to simulate what the inferred causal direction would be for all
values within these bounds. To evaluate how reliable, \(R\), the
inference of the causal direction is to potential measurement
imprecision in \(x\) and \(y\) we integrate over the simulated \(R\)
values for the possible measurement error values which are compatible
with the direction of causality obtained empirically from the Steiger
test. We also do the same for the measurement error values which are not
compatible. The ratio of these quantities is an indication of how much
of the measurement error space supports the inferred causal direction. A
ratio \(R=1\) indicates that the Steiger test is highly sensitive to
measurement error, with equal weight of the measurement error parameter
space supporting both directions of causality. Full details are provided
in Appendix 2 and Figure 3a.

@@

In the causal inference test (CIT), an omnibus p-value is generated from
four hypothesis tests: 1) \(g\) is associated with \(x\); 2) \(g\) is
associated with \(y\); 3) \(x\) is associated with \(y\); and 4) \(g\)
is independent of \(y|x\). The 4th condition employs mediation for
causal inference, and can be expressed as \(cov(g, y - \hat{y}) = 0\),
where \(\hat{y} = \hat{\alpha}_x + \hat{\beta}_x x_o\). When measurement
error in scale and imprecision is introduced, such that \(y_o\) is the
measured value of \(y\), it can be shown using basic covariance
properties (Appendix 1) that

@@

We performed simulations to compare the performance of MR against CIT in
detecting a causal association between simulated variables under
different levels of imprecision simulated in the exposure. Figure 4
shows the true positive rates between the CIT and MR for detecting a
causal association. We observe that the CIT has lower power in all
cases, with performance declining as measurement imprecision increases
in the exposure. When MR assumptions are satisfied, notably that it is
known on which of \(x\) and \(y\) the SNP \(g\) has a primary influence,
the performance of MR in detecting an association is unrelated to
measurement error in the exposure. Measurement error in the outcome does
reduce power, but does not induce a substantive difference in
performance between CIT and MR.

@@

If we do not know whether the SNP \(g\) has a primary influence on \(x\)
or \(y\) then CIT can attempt to infer the causal direction. Here we
introduce the MR Steiger approach to also orient the direction of
causality in an MR analysis when the underlying biology of the SNP is
not fully understood.

We show that in the presence of measurement imprecision,
\(d = \rho_{x, x_o} - \rho_{x,y}\rho_{y,y_o}\) (Appendix 2), where \(d\)
is a metric of the degree to which the Steiger test is liable to provide
the wrong estimate (\emph{i.e.} if \(d>0\) then the Steiger test is
likely to be correct about the causal direction). Thus it is important
to note that under certain conditions when measurement imprecision is
present the Steiger test could make erroneous inference about the causal
direction because the value of \(d\) is not restricted to being greater
than 0. However Figure 7 shows that when there is no measurement error
in \(x\), the Steiger test is unlikely to infer the wrong direction of
causality even if there is measurement error in \(y\). It also shows
that in most cases where \(x\) is measured with error, especially when
the causal effect between \(x\) and \(y\) is not very large, the
sensitivity of the Steiger test to measurement error is relatively low.

We performed simulations to explore the performance of this approach in
comparison to CIT in terms of the rate at which a strong causal
relationship is obtained for the correct direction of causality, and the
rate at which a strong causal relationship is obtained where the
reported direction of causality is incorrect. Simulations were performed
for two models, one for a ``causal model'' where there was a causal
relationship between \(x\) and \(y\); and one for a ``non-causal model''
where \(x\) and \(y\) were not causally related, but had a confounded
association induced by the SNP \(g\) influencing a confounder variable
\(u\).

Figure 5a shows that, for the ``causal model'', when \(d < 0\) the MR
analysis is indeed liable to infer the wrong direction of causality, and
that this erroneous result is more likely to occur with increasing
sample size. However, the CIT is in general more fallable to reporting a
robust causal association for the wrong direction of causality. When
\(d > 0\) is satisfied we observe that in most cases the MR method has
greater power to obtain evidence for causality than CIT, and always
obtains the correct direction of causality. The CIT, unlike the Steiger
test for MR, is able to distinguish the ``non-causal model'' from the
``causal model'' (Methods, Figure 5b), but it is evident that
measurement error will often lead the CIT to evaluate this confounding
model as being causal.

@@

We used the Steiger test to infer the direction of causality between DNA
methylation levels and gene expression levels and found that the causal
direction commonly goes in both directions (Figure 6a), but assuming no
or equal measurement error DNA methylation levels were the predominant
causal factor (\(p = 1.3\times 10^{-5}\)). We then went on to predict
the causal directions of the associations for varying levels of possible
measurement error. Figure 6a shows that the qualitative result of which
of DNA methylation or gene expression is more commonly the causal factor
is very strongly determined by measurement error.

@@

Mediation based network approaches, that go beyond analyses of two
variables, are very well established\textsuperscript{33} and have a
number of extensions that make them valuable tools, including for
example network construction. But because they are predicated on the
basic underlying principles of mediation they are liable to suffer from
the same issues of measurement error. Recent advances in MR methodology,
for example applying MR to genetical genomics\textsuperscript{47},
multivariate MR\textsuperscript{48} and mediation through
MR\textsuperscript{49--51} may offer more robust alternatives for these
more complicated problems.

@@

@@

Figure 3: a) We can predict the values the Steiger test would take
(z-axis) for different potential values of measurement error (x and y
axes), drawn here as the blue surface. When \(\rho_{g,y} > \rho_{g,x}\),
as denoted by range of values where the blue surface is above the red
plane, those values of measurement error lead to our observed Steiger
test inferring the wrong causal direction. Where the blue surface lies
below the red plane, these measurement error values support the inferred
causal direction of X to Y. A measure of reliability, therefore, is the
ratio of the negative and positive volumes of the total space bound by
the blue and red surfaces, \(R = \frac{V_{z \geq 0}}{ - V_{z < 0} }\).
In this case, where \(\rho_{g,x}^2 = 0.01\) and \(\rho_{x,y}^2 = 0.1\),
the \(R = 4.40\), which means that 4.40 times as much of the possible
measurement error values are in support of the \(x \rightarrow y\)
direction of causality than \(y \rightarrow x\). b) The influence of
\(\rho_{x,y}\) (x-axis) on the Steiger reliability values (y-axis) for
different values of \(\rho_{g,x}^2\). Inferring the direction of
causality is more sensitive to measurement error when there are stronger
causal associations between X and Y.

Figure 4: Outcomes were simulated to be causally influenced by exposures
with varying degrees of measurement imprecision applied to the exposure
variable (x axis). True positive rates (y axis) for MR and CIT were
compared for varying levels of measurement imprecision in the outcome
variable (rows of boxes) and sample sizes (columns of boxes).

@@

If \(R=1\) then the direction of causality is equally probable across
the range of possible measurement error values. If \(R > 1\) then \(R\)
times as much of the weighted parameter space favours the inferred
direction of causality. \(V_{z}\), the total volume of the function
(Figure 3), can be obtained analytically by solving:

@@

\hypertarget{ref-Ashenfelter1994}{}
29. Ashenfelter, O. \& Krueger, A. B. Estimates of the Economic Return
to Schooling from a New Sample of Twins. \emph{The American Economic
Review} \textbf{84,} 1157--1173 (1994).

\hypertarget{ref-Nagarajan2013}{}
30. Nagarajan, R. \& Scutari, M. Impact of noise on molecular network
inference. \emph{PloS one} \textbf{8,} e80735 (2013).

\hypertarget{ref-Shpitser2010}{}
31. Shpitser, I., VanderWeele, T. \& Robins, J. On the validity of
covariate adjustment for estimating causal effects. \emph{Proceedings of
the Twenty Sixth Conference on Uncertainty in Artificial Intelligence
(UAI-10)} 527--536 (2010).

\hypertarget{ref-Wang2015}{}
32. Wang, L. \& Michoel, T. Detection of regulator genes and eQTLs in
gene networks. \emph{arXiv} \textbf{arXiv:1512,} (2015).

\hypertarget{ref-Lagani2015}{}
33. Lagani, V., Triantafillou, S., Ball, G., Tegner, J. \& Tsamardinos,
I. in \emph{Uncertainty in biology: A computational modeling approach}
47 (Springer, 2015). at
\textless{}\href{https://books.google.com/books?id=8SLUCgAAQBAJ\%7B/\&\%7Dpgis=1}{https://books.google.com/books?id=8SLUCgAAQBAJ\{\textbackslash{}\&\}pgis=1}\textgreater{}

\hypertarget{ref-Lawlor2017}{}
34. Lawlor, D. A., Tilling, K. \& Davey Smith, G. Triangulation in
aetiological epidemiology. \emph{International Journal of Epidemiology}
\textbf{19,} dyw314 (2017).

\hypertarget{ref-Pierce2012}{}
35. Pierce, B. L. \& VanderWeele, T. J. The effect of non-differential
measurement error on bias, precision and power in Mendelian
randomization studies. \emph{International Journal of Epidemiology}
\textbf{41,} 1383--1393 (2012).

>>>>

An established study design that can provide information about causality
is randomisation. Given the hypothesis that trait A (henceforth referred
to as the exposure) is causally related to trait B (henceforth referred
to as the outcome), randomisation can be employed to assess the causal
nature of the association by randomly splitting the sample into two
groups, subjecting one group to the exposure and treating the other as a
control. The association between the exposure and the outcome in this
setting provides a robust estimate of the causal relationship. This
provides the theoretical basis behind randomised control trials, but in
practice randomisation is often impossible to implement in an
experimental context due to cost, scale or inability to manipulate the
exposure. The principle, however, can be employed in extant
observational data through the use of genetic variants associated with
the exposure (instruments), where the inheritance of an allele serves as
a random lifetime allocation of differential exposure
levels\textsuperscript{15,16}. Two statistical approaches to exploiting
the properties of genetic instruments are widely used: mediation-based
approaches and Mendelian randomisation (MR).

@@

MR has some important advantages over the mediation-based approaches.
The mediation-based approaches require that the exposure, outcome and
instrumental variables are all measured in the same data, whereas recent
extensions to MR circumvent this requirement, allowing causal inference
to be drawn when exposure variables and outcome variables are measured
in different samples\textsuperscript{28}. This has the crucial advantage
of improving statistical power by allowing analysis in much larger
sample sizes, and dramatically expands the breadth of possible
phenotypic relationships that can be evaluated\textsuperscript{26}.
Additionally, when MR assumptions are satisfied the method is robust to
there being measurement error in the exposure
variable\textsuperscript{29}. Indeed instrumental variable (IV) analysis
was in part initially introduced as a correction for measurement error
in the exposure\textsuperscript{30}, whereas it has been noted that both
classic mediation-based analyses\textsuperscript{13,14,31,32} and
mediation-based methods that use instrumental
variables\textsuperscript{33,34} are prone to be unreliable in its
presence.

Using theory and simulations we show how non-differential measurement
error in phenotypes can lead to unreliable causal inference in the
mediation-based CIT method. We then present an extension to MR that
allows researchers to ascertain the causal direction of an association
even when the biology of the instruments are not fully understood, and
also a matric to evaluate the sensitivity of the result of this
extension to measurement error. Together these extensions improve the
utility of MR in cases where mediation based methods might have
otherwise been used preferentially. Finally, we apply this new method to
infer the direction of causation between DNA methylation levels and gene
expression levels. Our analyses highlight that because these different
causal inference techniques have varying strengths and weaknesses,
triangulation of evidence from as many sources as possible should be
practiced in causal inference\textsuperscript{35}.

@@

where \(\beta_{MR} \neq 0\) denotes the existence of causality, and
\(\beta_{MR}\) is an estimate of the causal effect.

Measurement error of an exposure can be modeled as a transformation of
the true value that leads to the observed value, \(x_o = f(x)\). For
example, following Pierce and VanderWeele\textsuperscript{29} we can
define

@@

where \(\alpha_{mx}\) and \(\beta_{mx}\) influence the error in the
measurement of \(x\) by altering its scale, and \(\epsilon_{mx}\)
represents the imprecision (or noise) in the measurement of \(x\). The
same model of measurement error can be applied to the outcome variable
\(y\). In this study we assume there is no measurement error in the SNP
and measurement error in the exposure and the outcome are uncorrelated.

@@

The method that we will now describe is designed to distinguish between
two models, \(x \rightarrow y\) or \(y \rightarrow x\). Unlike the CIT
framework, this approach cannot infer if the true model is
\(x \leftarrow g \rightarrow y\). We also assume all genetic effects are
additive.

@@

The Steiger test for inferring if \(x \rightarrow y\) is based on
evaluating \(\rho_{gx} > \rho_{gy}\). However, \(\rho_{gx}\) and
\(\rho_{gy}\) are underestimated if \(x\) and \(y\) are measured
imprecisely. If, for example, \(x\) has lower measurement precision than
\(y\) then we might empirically obtain \(\rho_{g,x_o} > \rho_{g,y_o}\).
As we show in the appendix, the maximum measurement error of \(x_o\) is
\(\rho_{g,x_o}\) and the minimum is 0 (same applies to \(y_o\)). It is
possible to simulate what the inferred causal direction would be for all
values within these bounds. To evaluate how reliable, \(R\), the
inference of the causal direction is to potential measurement
imprecision in \(x\) and \(y\) we integrate over the simulated \(R\)
values for the possible measurement error values which are compatible
with the direction of causality obtained empirically from the Steiger
test. We also do the same for the measurement error values which are not
compatible. The ratio of these quantities is an indication of how much
of the measurement error space supports the inferred causal direction. A
ratio \(R=1\) indicates that the Steiger test is highly sensitive to
measurement error, with equal weight of the measurement error parameter
space supporting both directions of causality. Full details are provided
in Appendix 2.

@@

In the causal inference test (CIT), the 4th condition (see Methods)
employs mediation for causal inference, and can be expressed as
\(cov(g, y - \hat{y}) = 0\), where
\(\hat{y} = \hat{\alpha}_x + \hat{\beta}_x x_o\). When measurement error
in scale and imprecision is introduced, such that \(y_o\) is the
measured value of \(y\), it can be shown using basic covariance
properties (Appendix 1) that

@@

We performed simulations to compare the performance of MR against CIT in
detecting a causal association between simulated variables under
different levels of imprecision simulated in the exposure. Figure 3
shows the true positive rates between the CIT and MR for detecting a
causal association. We observe that the CIT has lower power in all
cases, with performance declining as measurement imprecision increases
in the exposure. When MR assumptions are satisfied, notably that it is
known on which of \(x\) and \(y\) the SNP \(g\) has a primary influence,
the performance of MR in detecting an association is unrelated to
measurement error in the exposure. Measurement error in the outcome does
reduce power, but does not induce a substantive difference in
performance between CIT and MR.

@@

If we do not know whether the SNP \(g\) has a primary influence on \(x\)
or \(y\) then CIT can attempt to infer the causal direction. Here we
introduce the MR Steiger approach to similarly orient the direction of
causality but in an MR analysis when the underlying biology of the SNP
is not fully understood.

For a particular association, it is of interest to identify the range of
possible measurement error values agree and disagree with the
empirically inferred causal direction (Figure 4a, Appendix 2). This
metric can be used to evaluate the reliability of MR Steiger.

We show that in the presence of measurement imprecision,
\(d = \rho_{x, x_o} - \rho_{x,y}\rho_{y,y_o}\) (Appendix 2) determines
the range of parameters around which the Steiger test is liable to
provide the wrong direction of causality (\emph{i.e.} if \(d>0\) then
the Steiger test is likely to be correct about the causal direction).
Figure 4b shows that when there is no measurement error in \(x\), the
Steiger test is unlikely to infer the wrong direction of causality even
if there is measurement error in \(y\). It also shows that in most cases
where \(x\) is measured with error, especially when the causal effect
between \(x\) and \(y\) is not very large, the sensitivity of the
Steiger test to measurement error is relatively low.

\subsubsection{Comparison of CIT and MR Steiger for obtaining the
correct direction of
causality}\label{comparison-of-cit-and-mr-steiger-for-obtaining-the-correct-direction-of-causality}

We used simulations to explore the performance of the MR Steiger
approach in comparison to CIT in terms of the rate at which a strong
causal relationship is obtained for the correct direction of causality,
and the rate at which a strong causal relationship is obtained where the
reported direction of causality is incorrect. Simulations were performed
for two models, one for a ``causal model'' where there was a causal
relationship between \(x\) and \(y\); and one for a ``non-causal model''
where \(x\) and \(y\) were not causally related, but had a confounded
association induced by the SNP \(g\) influencing a confounder variable
\(u\).

Figure 5a shows that, for the ``causal model'', when \(d < 0\) the MR
analysis is indeed liable to infer the wrong direction of causality, and
that this erroneous result is more likely to occur with increasing
sample size. However, the CIT is in general more fallable to reporting a
robust causal association for the wrong direction of causality. When
\(d > 0\) is satisfied we observe that in most cases the MR method has
greater power to obtain evidence for causality than CIT, and always
obtains the correct direction of causality. The CIT, unlike the Steiger
test for MR, is able to distinguish the ``non-causal model'' from the
``causal model'' (Methods, Figure 5b), but it is evident that
measurement error will often lead the CIT to evaluate erroneously this
confounding model as being causal.

@@

We used the Steiger test to infer the direction of causality between DNA
methylation levels and gene expression levels and found that the causal
direction commonly goes in both directions (Figure 6a), but assuming no
or equal measurement error, DNA methylation levels were the predominant
causal factor (\(p = 1.3\times 10^{-5}\)). We then went on to predict
the causal directions of the associations for varying levels of possible
measurement error. Figure 6a shows that the qualitative result of which
of DNA methylation or gene expression is more commonly the causal factor
is very strongly determined by measurement error.

@@

Mediation based network approaches, that go beyond analyses of two
variables, are very well established\textsuperscript{34} and have a
number of extensions that make them valuable tools, including for
example network construction. But because they are predicated on the
basic underlying principles of mediation they are liable to suffer from
the same issues of measurement error. Recent advances in MR methodology,
for example applying MR to genetical genomics\textsuperscript{47},
multivariate MR\textsuperscript{48} and mediation through
MR\textsuperscript{49--51} may offer more robust alternatives for these
more complicated problems.

@@

Figure 3: Outcomes were simulated to be causally influenced by exposures
with varying degrees of measurement imprecision applied to the exposure
variable (x axis). True positive rates (y axis) for MR and CIT were
compared for varying levels of measurement imprecision in the outcome
variable (rows of boxes) and sample sizes (columns of boxes).

@@

Figure 4: a) We can predict the values the Steiger test would take
(z-axis) for different potential values of measurement error (x and y
axes), drawn here as the blue surface. When \(\rho_{g,y} > \rho_{g,x}\),
as denoted by range of values where the blue surface is above the red
plane, those values of measurement error lead to our observed Steiger
test inferring the wrong causal direction. Where the blue surface lies
below the red plane, these measurement error values support the inferred
causal direction of X to Y. A measure of reliability, therefore, is the
ratio of the negative and positive volumes of the total space bound by
the blue and red surfaces, \(R = \frac{V_{z \geq 0}}{ - V_{z < 0} }\).
In this case, where \(\rho_{g,x}^2 = 0.01\) and \(\rho_{x,y}^2 = 0.1\),
the \(R = 4.40\), which means that 4.40 times as much of the possible
measurement error values are in support of the \(x \rightarrow y\)
direction of causality than \(y \rightarrow x\). b) Plots depicting the
parameter space in which the function
\(d = cor(x, x_O) - cor(x,y)cor(y, y_O)\) is negative. When \(d\) is
negative the Steiger test is liable to infer the wrong direction of
causality. Shaded regions show the parameter space where \(d\) is
negative. The graph shows that for the majority of the parameter space
of the function, \(d\) is positive, especially where causal
relationships are relatively weak.

@@

If \(R=1\) then the direction of causality is equally probable across
the range of possible measurement error values. If \(R > 1\) then \(R\)
times as much of the weighted parameter space favours the inferred
direction of causality. \(V_{z}\), the total volume of the function
(Figure 4), can be obtained analytically by solving:

@@

\hypertarget{ref-Pierce2012}{}
29. Pierce, B. L. \& VanderWeele, T. J. The effect of non-differential
measurement error on bias, precision and power in Mendelian
randomization studies. \emph{International Journal of Epidemiology}
\textbf{41,} 1383--1393 (2012).

\hypertarget{ref-Ashenfelter1994}{}
30. Ashenfelter, O. \& Krueger, A. B. Estimates of the Economic Return
to Schooling from a New Sample of Twins. \emph{The American Economic
Review} \textbf{84,} 1157--1173 (1994).

\hypertarget{ref-Nagarajan2013}{}
31. Nagarajan, R. \& Scutari, M. Impact of noise on molecular network
inference. \emph{PloS one} \textbf{8,} e80735 (2013).

\hypertarget{ref-Shpitser2010}{}
32. Shpitser, I., VanderWeele, T. \& Robins, J. On the validity of
covariate adjustment for estimating causal effects. \emph{Proceedings of
the Twenty Sixth Conference on Uncertainty in Artificial Intelligence
(UAI-10)} 527--536 (2010).

\hypertarget{ref-Wang2015}{}
33. Wang, L. \& Michoel, T. Detection of regulator genes and eQTLs in
gene networks. \emph{arXiv} \textbf{arXiv:1512,} (2015).

\hypertarget{ref-Lagani2015}{}
34. Lagani, V., Triantafillou, S., Ball, G., Tegner, J. \& Tsamardinos,
I. in \emph{Uncertainty in biology: A computational modeling approach}
47 (Springer, 2015). at
\textless{}\href{https://books.google.com/books?id=8SLUCgAAQBAJ\%7B/\&\%7Dpgis=1}{https://books.google.com/books?id=8SLUCgAAQBAJ\{\textbackslash{}\&\}pgis=1}\textgreater{}

\hypertarget{ref-Lawlor2017}{}
35. Lawlor, D. A., Tilling, K. \& Davey Smith, G. Triangulation in
aetiological epidemiology. \emph{International Journal of Epidemiology}
\textbf{19,} dyw314 (2017).
